\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-03-16 latex/paper.tex
Edits from personal reading and Brill's comments

% title font size
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

@@

    \section{Summary}
    Cilia are sensory organelles that are essential for human development
    and physiology \citep{satir2010primary, marshall2006cilia}.
    They function primarily by relaying extracellular cues to cells
    \citep{satir2010primary},
    but can also act as motile propellers in certain cell types
    \citep{bloodgood2010sensory}.
    A large number of genetic disorders linked to cilium dysfunction are
    associated with proteins that localize to the cilium transition zone (TZ),
    a structure at the base of cilia that regulates trafficking in and out
    of the cilium \citep{reiter2012base, szymanska2012transition}.
    Although substantial effort has been undertaken
    to elucidate TZ proteins and their functions in cilium assembly and function,
    processes underlying maturation of TZs are not well understood.
    Here, we report a role for the membrane lipid
    phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) in TZ maturation and length regulation
    in the \textit{Drosophila melanogaster} male germline.
    We show that reduction of cellular \PIP{} levels
    by expression of the Salmonella phosphoinositide phosphatase SigD,
    or mutation of
    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl),
    induces the formation of longer than normal TZs.
    These hyperelongated TZs exhibit signs of functional defects,
    such as the inability
    to be migratory \citep{basiri2014migrating} and loss of membrane tethering.
    We also report that the \textit{onion rings} (\textit{onr}) allele
    of the Drosophila Exo84
    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
    by promoting proper TZ maturation.

    \section{Results}
    Cilia are sensory organelles that are present on almost all cells in the human body
    \citep{satir2010primary, marshall2006cilia}.
    They function in signal reception and transduction in response to extracellular cues,
    but also have roles in cellular and extracellular fluid motility
    \citep{brooks2014multiciliated, marshall2006cilia},
    for example, as the sperm flagellum.
    Consistent with their importance in cell signalling,
    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
    known collectively as ciliopathies, which can display
    neurological defects \citep{valente2014primary},
    skeletal abnormalities \citep{hammarsjo2017novel},
    and infertility \citep{inaba2016sperm}, in addition to other phenotypes
    \citep{waters2011ciliopathies}.
    Many ciliopathies are associated with mutations in proteins that localize
    to the transition zone (TZ), the proximal-most region of the cilium that
    functions as a diffusion barrier and regulates the
    bidirectional transport of protein cargo at the base of the cilium
    \citep{reiter2012base, szymanska2012transition}.
    The TZ is essential for ciliogenesis and function.
    For example, the conserved TZ protein CEP290 is mutated in at least
    six different ciliopathies that lie on a spectrum of clinical features and severities
    and is important for cilium formation
    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
    and Drosophila \citep{basiri2014migrating}.
    Although the protein composition of TZs has been investigated in various
    studies ranging from single gene analysis to proteomics,
    the process of maturation of the TZ, through which it is converted from an
    immature form to one competent at supporting
    cilium assembly, is relatively understudied.

    Ciliogenesis begins with assembly of a nascent TZ at the tip of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
    and the TZ, in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    \textit{Paramecium} \citep{aubusson2015transition},
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

@@

    %
    %   Results - 1
    %
    \subsection{\PIP{} is essential for transition zone maturation}
    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter (referred to herein as \sigd{}),
    \citep{wei2008depletion}.
    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these defects were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged versions of the
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes.
    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase
    when TZs are still immature.
    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
    compared to wild-type controls by the end of the G2 phase following
    the period of TZ maturation in spermatocytes (Figure 1B and 1C).
    Unlike Drosophila \textit{cep290} mutants, which contain
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    We previously showed that the structure of basal bodies
    from electron microscopy is normal, and that the localization of the centriolar
    marker GFP-PACT \citep{basto2006flies}
    is similar in controls and \sigd{} \citep{wei2008depletion}.
    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    exhibited hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes, visualized by staining for acetylated tubulin, were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    is frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    %
    %   Results - 2
    %
    \subsection{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
    Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can also dephosphorylate other PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype in response to decreased \PIP{},
    we attempted to rescue the TZ phenotype by
    co-expressing \sigd{} with
    fluorescently-tagged Skittles (Sktl)
    using the same $\beta$\textsubscript{2}-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and B).
    We also found that \textit{sktl} clones made
    using Flp/FRT-based mitotic recombination and expressing the
    basal body and TZ marker Unc
    \citep{baker2004mechanosensory, wei2008depletion}
    exhibited TZ hyperelongation (Figure 2C),
    suggesting that Sktl is important for TZ maturation.

    A previous report showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    Drosophila PIPKIs arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$
    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline,
    but not TZ assembly. 
    Notably, neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    and is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
    \citep{franz2013cp110}.

    %
    %   Results - 3
    %
    \subsection{Hyperelongated transition zones exhibit signs of functional defects}
    We sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    During cell elongation following meiosis, the TZ detaches from
    the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is presumably incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    As shown by Unc and Cep290 localization,
    TZs that assembled in \sigd{} cells were frequently incapable of detaching from
    the basal body and migrating along the axoneme despite
    axoneme elongation (Figure 1E) and cellular elongation
    (Figures 3A and 3B).
    We previously described ``comet-shaped'' localization of Unc-GFP in these cells,
    and we find that these hyperelongated Unc signals persist during cellular elongation
    despite elongation of the axoneme (Figure 3A bottommost panel and Figure 1E).

@@

    %
    %   Results - 4
    %
    \subsection{The \textit{onion rings} mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    Unlike \sigd{}, the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membranes were affected in \sigd{}
    or \textit{onr} mutants in a manner similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to either establish or maintain
    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that the exocyst, and Exo84 in particular, regulates
    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

    \section{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional one,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base}.
    In the Drosophila male germline, TZ maturation occurs during the
    extended G2 phase in spermatocytes prior to meiosis, and can be readily
    observed by an increase in TZ length using fluorescence microscopy.
    Our results suggest that normal execution of this process
    requires \PIP{}, and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Regulation of TZ length in the Drosophila male germline has been reported
    previously.
    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
    whereas
    \textit{cby; dila} and \textit{cby} mutants display hyperelongated TZs
    \citep{enjolras2012drosophila,vieillard2016transition}.
    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} seems to be intimately involved in this process as well, but it does
    so independantly of Cby and Mks1.

@@

    In this study, we report two phenotypes associated with
    hyperelongated TZs that we postulate to be indicators of
    TZ dysfunction.
    Firstly, we show that hyperelongated TZs are unable to
    detach from basal bodies at the onset of axoneme elongation
    in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
    Nonetheless, axonemes can assemble despite the lack of a functional
    TZ or membrane association in \sigd{} cells.
    As we previously reported, these axonemes frequently exhibit aberrant
    ultrastructure \citep{wei2008depletion}.
    This is similar to \textit{cep290} \citep{basiri2014migrating}
    and \textit{dila}; \textit{cby} \citep{vieillard2016transition}
    mutants,
    which can assemble spermatid axonemes despite lacking
    functional TZs.

@@

    \section{Methods}
    \subsection{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion}.
    GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
    and transgenic flies were generated using standard \textit{P} element-mediated transformation.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

    \subsection{Antibodies}
    The following primary antibodies were used for immunofluorescence
    at the indicated concentrations ---
    chicken anti-GFP IgY (abcam) 1:1000;
    rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
    rabbit anti-Centrin (C7736, Sigma-Aldrich), 1:500;
    mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
    Secondary antibodies were Alexa 488- and Alexa 568-conjugated
    anti-mouse, anti-rabbit and anti-chicken
    IgG (Molecular Probes) at 1:1000.
    DAPI at 1:1000 was used to stain for DNA.

    \subsection{Fluorescence microscopy}
    For live imaging, testes were dissected in phosphate buffered saline (PBS).
    To stain for DNA, intact testes were incubated in PBS with
    Hoechst (1:5000) for 5 minutes.
    Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
    ruptured using a syringe needle and
    squashed under a glass coverslip using Kimwipes.
    The edges of the coverslip were sealed with nail polish
    and the specimen was visualized using an epifluorescence microscope.

@@

    \subsection{Statistical methods}
    Statistical analysis and graphing was performed using R (version 3.4)
    \citep{r}.
    A Gaussian jitter was applied when plotting
    results in Figures 1 and 2 for clearer visualization of trends,
    but raw data was used for all analyses.
    Statistical tests for ``absence of phenotype'' were computed using a binomial test
    under the assumption that the probability of the phenotype occuring was fixed.
    All $t$-tests were unpaired and two-sided with Welch's correction for unequal variances.
    $n$ represents the pooled number of samples from multiple biological replicates.
    A significance level of 0.01 was fixed \textit{a priori} for all classical analyses.
    All raw data and code for analysis and plotting can be found online
    at \url{http://www.github.com/alindgupta/germline-paper/}.

>>>>

% title font size
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries\itshape}

@@

    \section*{Summary}
    Cilia are sensory organelles that are essential for human development
    and physiology \citep{satir2010primary, marshall2006cilia}.
    They function primarily by relaying extracellular cues to cells
    \citep{satir2010primary, bloodgood2010sensory},
    but can also act as motile propellers in certain cell types
    \citep{eley2005cilia}.
    A large number of genetic disorders linked to cilium dysfunction are
    associated with proteins that localize to the cilium transition zone (TZ),
    a structure at the base of cilia that regulates trafficking in and out
    of the cilium \citep{reiter2012base, szymanska2012transition}.
    Although substantial effort has been undertaken
    to elucidate TZ proteins and their functions in cilium assembly and function
    \citep{gonccalves2017ciliary},
    processes underlying maturation of TZs are not well understood.
    Here, we report a role for the membrane lipid
    phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) in TZ maturation and length regulation
    in the \textit{Drosophila melanogaster} male germline.
    We show that reduction of cellular \PIP{} levels
    by expression of the Salmonella phosphoinositide phosphatase SigD,
    or mutation of
    the type I phosphatidylinositol phosphate kinase (PIPKI) Skittles (Sktl),
    induces the formation of longer than normal TZs.
    These hyperelongated TZs exhibit signs of functional defects,
    such as the inability
    to be migratory \citep{basiri2014migrating} and loss of plasma membrane tethering.
    We also report that the \textit{onion rings} (\textit{onr}) allele
    of the Drosophila Exo84
    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
    by promoting proper TZ maturation.

    \section*{Results}
    Cilia are sensory organelles that are present on almost all cells in the human body
    \citep{satir2010primary, marshall2006cilia}.
    They function in signal reception and transduction in response to extracellular cues,
    but also have roles in cellular and extracellular fluid motility
    \citep{marshall2006cilia, eley2005cilia, brooks2014multiciliated},
    for example, as the sperm flagellum.
    Consistent with their importance in cell signalling,
    defects in cilium formation (i.e. ciliogenesis) are associated with genetic disorders
    known collectively as ciliopathies, which can display
    neurological defects \citep{valente2014primary},
    skeletal abnormalities \citep{hammarsjo2017novel},
    and infertility \citep{inaba2016sperm}, in addition to other phenotypes
    \citep{waters2011ciliopathies}.
    Many ciliopathies are associated with mutations in proteins that localize
    to the transition zone (TZ), the proximal-most region of the cilium that
    functions as a diffusion barrier and regulates the
    bidirectional transport of protein cargo at the base of the cilium
    \citep{reiter2012base, szymanska2012transition}.
    The TZ is essential for ciliogenesis and function.
    For example, the conserved TZ protein CEP290 is mutated in at least
    six different ciliopathies
    \citep{rachel2012photoreceptor} that lie on a spectrum of clinical features and severities
    and is important for cilium formation
    and function in both humans \citep{shimada2017vitro, stowe2012centriolar}
    and Drosophila \citep{basiri2014migrating}.
    Although the protein composition of TZs has been investigated in various
    studies ranging from single gene analysis to proteomics \citep{gonccalves2017ciliary},
    the process of maturation of the TZ, through which it is converted from an
    immature form to one competent at supporting
    cilium assembly, is relatively understudied.

    Ciliogenesis begins with assembly of a nascent TZ at the tip of
    the basal body \citep{reiter2012base}.
    This nascent TZ undergoes maturation, during which its structure and protein
    composition changes, allowing for the
    establishment of a compartmentalized ciliary space, bounded by the ciliary membrane
    and the TZ, in which axoneme assembly and signalling can occur.
    The axoneme is a microtubule-based structure that forms the core of all cilia and flagella.
    In the Drosophila male germline, nascent TZs first assemble on basal bodies
    during early G2 phase in spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with anchoring of cilia to the plasma membrane,
    rearrangment of microtubules within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    Paramecium \citep{aubusson2015transition},
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    \textit{Drosophila melanogaster} \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

@@

    %
    %   Results - 1
    %
    \subsection*{\PIP{} is essential for transition zone maturation}
    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella phosphoinositide phosphatase SigD
    under the control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
    (referred to herein as \sigd{})
    \citep{wei2008depletion}.
    Note that \sigd{} corresponds to ``SigD-high'' in \citep{fabian2010phosphatidylinositol}.
    SigD dephosphorylates \PIP{} \textit{in vivo},
    and we previously showed that \sigd{} induces male sterility
    due in part to defects in flagellar biosynthesis \citep{wei2008depletion}.
    To examine whether these defects were caused by aberrant TZ function,
    we examined the localization of fluorescently-tagged versions of the
    centriolar/basal body protein
    Ana1 (homolog of CEP295) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly in spermatocytes.
    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase
    when TZs are still immature.
    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
    compared to wild-type controls by the end of G2 phase following
    the period of TZ maturation in spermatocytes (Figure 1B and 1C).
    Unlike Drosophila \textit{cep290} mutants, which contain
    longer than normal basal bodies \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1C).
    We previously showed that the structure of basal bodies in \sigd{}
    from electron microscopy is normal, and that the localization of the centriolar
    marker GFP-PACT \citep{basto2006flies}
    is similar in controls and \sigd{} \citep{wei2008depletion}.
    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition}
    exhibited hyperelongation in \sigd{} (Figure 1D),
    suggesting that this phenotype is not specific to Cep290 but is shared
    by other members of the Drosophila TZ.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%
    in spermatocytes at late G2 phase)
    and showed high intra-cyst correlation (\textgreater 0.95) suggestive
    of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite the persistence of hyperelongated TZs through meiosis,
    axonemes, visualized by staining for acetylated tubulin, were able to
    elongate normally in post-meiotic cells (Figure 1E).
    However, as we showed previously, the ultrastructure of these axonemes
    is frequently aberrant,
    either lacking symmetry completely or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    %
    %   Results - 2
    %
    \subsection*{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
    Whereas \PIP{} is the major substrate for SigD in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can also dephosphorylate other PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype in response to decreased \PIP{},
    we attempted to rescue the TZ phenotype by
    co-expressing \sigd{} with
    fluorescently-tagged Skittles (Sktl)
    using the same $\beta$\textsubscript{2}-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and 2B).
    We also found that \textit{sktl} clones made
    using Flp/FRT-based mitotic recombination and expressing the
    basal body and TZ marker Unc
    \citep{baker2004mechanosensory, wei2008depletion}
    exhibited TZ hyperelongation at a low penetrance (Figure 2C),
    suggesting that Sktl is important for TZ maturation.
    Note that the \textit{sktl}$^{2.3}$ allele used for making mitotic clones
    is a hypomorph \citep{gervais2008pip5k}.

    A previous report showed the vertebrate PIPKI$\gamma$ to be
    important for cilium formation in cultured cell lines
    \citep{xu2014pipkigamma}.
    The two Drosophila PIPKIs, namely Sktl and PIP5K59B,
    arose from the recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$
    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
    by promoting CP110 removal from basal bodies \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length in the Drosophila male germline,
    but not TZ assembly. 
    Notably, neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    and is removed from basal bodies in the earliest stages of G2 phase in the Drosophila male germline
    \citep{franz2013cp110}.

    %
    %   Results - 3
    %
    \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
    We sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    During cell elongation following meiosis in the Drosophila male germline, the TZ detaches from
    the basal body and migrates along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is presumably incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    As shown by Unc and Cep290 localization,
    TZs that assembled in \sigd{} cells were frequently incapable of detaching from
    the basal body and migrating along the axoneme despite
    axoneme elongation (Figure 1E) and cellular elongation
    (Figures 3A and 3B).
    We previously described ``comet-shaped'' localization of Unc-GFP in these cells
    \citep{wei2008depletion},
    and we find that these hyperelongated Unc signals persist during cellular elongation
    despite elongation of the axoneme (Figure 3A bottommost panel and Figure 1E).

@@

    %
    %   Results - 4
    %
    \subsection*{The onion rings mutant decouples defects found in cells with reduced levels of \PIP{}}
    We previously showed that male flies homozygous for the \textit{onion rings}
    (\textit{onr}) mutant of Drosophila Exo84 were sterile, and had phenotypes
    similar to \sigd{} such as defects in cell polarity \citep{wei2008depletion}.
    Exo84 is a component of the octameric exocyst complex, which binds
    \PIP{} and regulates membrane trafficking at the plasma membrane.
    To investigate whether defects in TZ hyperelongation could be explained by
    defective Exo84 function, we examined TZs in \textit{onr} mutants.
    Unlike \sigd{}, the \textit{onr} mutant did not display hyperelongated TZs (Figure 4C),
    suggesting that Exo84 is dispensable for TZ maturation.

    Due to involvement of exocyst in membrane trafficking at the plasma membrane,
    we examined whether cilium-associated membranes were affected in \sigd{}
    or \textit{onr} mutants in a manner similar to \textit{dila; cby} mutants
    \citep{vieillard2016transition}.
    Whereas TZs in \sigd{} and \textit{onr} cells anchored properly
    to the plasma membrane, they were unable to maintain
    membrane connections, and were rendered cytoplasmic (Figure 4A and B) similar to
    \textit{dila; cby} mutants.
    Although we were not able to determine the localization of Exo84 due to the
    lack of available reagents,
    we found that GFP-tagged Exo70 localized to centrioles (Figure 4D).
    Exo70 can directly bind to \PIP{} and mediates the recruitment of
    the exocyst complex to the plasma membrane \citep{he2007exo70}.
    Our results suggest that the exocyst, and Exo84 in particular, regulates
    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

    \section*{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional one,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base, gonccalves2017ciliary}.
    In the Drosophila male germline, TZ maturation occurs during the
    extended G2 phase in spermatocytes prior to meiosis, and can be readily
    observed by an increase in TZ length using fluorescence microscopy.
    Our results suggest that normal execution of this process
    requires \PIP{}, and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Regulation of TZ length in the Drosophila male germline has been reported
    previously.
    For example, \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila},
    whereas
    \textit{cby; dila} and \textit{cby} mutants display hyperelongated TZs
    \citep{enjolras2012drosophila,vieillard2016transition}.
    Since both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} seems to be intimately involved in this process as well, but it does
    so independantly of Cby and Mks1.

@@

    In this study, we report two phenotypes associated with
    hyperelongated TZs that we hypothesize to be indicators of
    dysfunction.
    Firstly, we show that hyperelongated TZs are unable to
    detach from basal bodies at the onset of axoneme elongation
    in spermatids, unlike TZs in normal cells \citep{basiri2014migrating, fabian2012drosophila}.
    Nonetheless, axonemes can assemble despite the lack of a functional
    TZ or membrane association in \sigd{} cells.
    As we previously reported, these axonemes frequently exhibit aberrant
    ultrastructure \citep{wei2008depletion}.
    This is similar to \textit{cep290} \citep{basiri2014migrating}
    and \textit{dila}; \textit{cby} \citep{vieillard2016transition}
    mutants,
    which can assemble spermatid axonemes despite lacking
    functional TZs.

@@

    \section*{Methods}
    \subsection*{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion}.
    GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
    and transgenic flies were generated using standard \textit{P} element-mediated transformation.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

    \subsection*{Antibodies}
    The following primary antibodies were used for immunofluorescence
    at the indicated concentrations ---
    chicken anti-GFP IgY (abcam) 1:1000;
    rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
    rabbit anti-Centrin (C7736, Sigma-Aldrich), 1:500;
    mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
    Secondary antibodies were Alexa 488- and Alexa 568-conjugated
    anti-mouse, anti-rabbit and anti-chicken
    IgG (Molecular Probes) at 1:1000.
    DAPI at 1:1000 was used to stain for DNA.

    \subsection*{Fluorescence microscopy}
    For live imaging, testes were dissected in phosphate buffered saline (PBS).
    To stain for DNA, intact testes were incubated in PBS with
    Hoechst (1:5000) for 5 minutes.
    Testes were transferred to a polylysine-coated glass slide in a drop of PBS,
    ruptured using a syringe needle and
    squashed under a glass coverslip using Kimwipes.
    The edges of the coverslip were sealed with nail polish
    and the specimen was visualized using an epifluorescence microscope.
    Cells were examined live whenever possible to avoid artefacts from immunostaining.

@@

    \subsection*{Statistical methods}
    Statistical analysis and graphing was performed using R (version 3.4)
    \citep{r}.
    A Gaussian jitter was applied when plotting
    results in Figures 1 and 2 for clearer visualization of trends,
    but raw data was used for all analyses.
    Statistical tests for ``absence of phenotype'' were computed using a binomial test
    under the assumption that the probability of the phenotype occuring was fixed.
    All $t$-tests were unpaired and two-sided with Welch's correction for unequal variances.
    $n$ represents the pooled number of samples from multiple biological replicates.
    A significance level of 0.01 was fixed \textit{a priori} for all classical analyses.
    All raw data and code for analysis and plotting can be found online
    at \url{http://www.github.com/alindgupta/germline-paper/}.

    \subsection*{Phylogenetic analysis}
    Candidate orthologs of Skittles and PIP5K9B were queried
    from Inparanoid (version 8.0) and FlyBase (version 2.0).
    Poorly annotated protein sequences were confirmed
    to encode type I phosphatidylinositol phosphate
    kinases using reciprocal BLAST search.
    Phylogeny.fr (\url{http://www.phylogeny.fr}) \citep{dereeper2008phylogeny} was used for
    phylogenetic reconstruction with T-Coffee for multiple alignment
    and MrBayes for tree construction.
    The output was converted to a vector image in Illustrator
    and colours were added for the purpose of illustration.
